Shape Inflation With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes

### 2013-04-26 documents/thesis/SIBGRAPI2013/TQLBO.tex

%------------------------------------------------------------------------- 
% change the % on next lines to produce the final camera-ready version 
\newif\iffinal
%\finalfalse
\finaltrue
\newcommand{\jemsid}{99999}
%-------------------------------------------------------------------------

@@

Interest in meshes composed of triangles and quads has lately increased
because of the flexibility of modeling tools such as Blender 3D \cite{blender}.
Nowadays, many artists use a manual connection of a couple of vertices
to perform animation processes and interpolation \cite{Mullen2007}.
It is then of paramount importance to develop operators that easily
interact with such meshes, eliminating the need of preprocessing the
mesh to convert it to triangles. The shape enhancement and shape exaggeration
can thus be used as such brush in the sculpting process, when inflating
a shape since current brushes end up by losing detail when moving
vertices \cite{Stanculescu2011}. In contrast, the presented method
inflates a mesh by moving the vertices towards the reverse curvature
direction, conserving the shape and sharp features of the model.

%------------------------------------------------------------------------- 
\paragraph*{Contributions}
%
This work presents an extension of the Laplace
Beltrami operator for hybrid quad/triangle meshes, representing a
larger mesh spectrum from what has been presented so far. The method
eliminates the need of preprocessing and allows preservation of the
original topology. Likewise, along with this operator, it is proposed
a method to generate a family of parameterized shapes, in a robust
and predictable way. This method enables customization of the smoothness
and curvature, obtained during the subdivision surfaces process. Finally,
it is proposed a new brush for enhancing the silhouette mesh features
in modeling and sculpting.

This work is organized as follows: Section \ref{sub:1.1-Related-work}
presents works related to the Laplacian mesh processing, digital sculpting,
and offsetting methods for polygonal meshes; In section \ref{sec:Laplacian-Smooth}
, it is described the theoretical framework of the Laplacian operator
for polygon meshes; In section \ref{sec:Proposed-Method}, it is presented
the method for shape enhancement and applications of subdivision of
surfaces and sculpting; finally some Laplacian operator results, to
hybrid quad/triangle meshes are graphically shown as well as results
of the shape enhancement applications in sculpting, subdivision and
modeling.

@@

Offset methods for polygon meshing, based on the curvature defined
by the Laplace Beltrami operator, have been developed. These methods
adjust the shape offset by a constant distance, with enough precision
as to minimize the Hausdorff error. Nevertheless, these methods fail
to conserve sufficient detail because of the smoothing, a crucial
issue which depends on the offset size \cite{Zhuo2012}. In volumetric
approaches, in case of point-based representations, the offset boundary
computation is based on the distance field and therefore when calculating
such offset, the topology of the model may be different to the original
\cite{Chen2011}.

\cite{Gal2009} propose automatic feature detection and shape edition
with feature inter-relationship preservation. They define salient
surface features like ridges and valleys, characerized by their first
and second order curvature derivatives \cite{Ohtake2004}, and angle-based
threshold. Likewise, curves have been also classified as planar or
non-planar, approximated by lines, circles, ellipses and other complex
shapes. In such case, the user defines an initial change over several
features which is propagated towards other features, based on the
classified shapes and the inter-relationships between them. This method
works well with objects that have sharp edges, composed of basic geometric
shapes such as lines, circles or ellipses. However, the method is
very limited when models are smooth since it cannot find the proper
features to edit.

@@

The \textit{Laplace Beltrami operator} LBO noted as $\triangle_{g}$
is used for measuring the mean curvature normal to the Surface $S$
\cite{Pinkall1993}.

\begin{equation}
\triangle_{g}S=2\kappa\mathbf{n}\label{eq:def_LBO}
\end{equation}

The LBO has desirable properties: the LBO points out to the direction
of the minimal surface area, minimizing the energy of the total surface
curvature $S$ at equation (\ref{eq:total_cuarvature_integral}).

@@

\begin{equation}
\triangle_{g}\left(v_{i}\right)=2\kappa\mathbf{n}=\frac{\nabla A}{A}=\underset{v_{j}\in N_{1}\left(v_{i}\right)}{\frac{1}{2A}\sum}w_{ij}\left(v_{j}-v_{i}\right)
\end{equation}

@@

\subsection{The Shape Enhancement\label{sub:Curvature-Enhancing}}

@@

\caption{\label{fig:Subdivision-Cups} Family of cups generated with our method,
from a coarse model (a), (c): the shape, obtained from the Catmull-Clark
Subdivision (b), (d), is enhanced. Soft constraints, over the coarse
model, is drawn in red and blue (c).}

@@

The shape is enhanced by using the reverse direction of the curvature
flow, moving the vertices towards those mesh portions with larger
curvature. A standard diffusion process is applied:

@@

The vertices $V^{t+1}$ are enhanced, along their reverse curvature
direction, by solving the linear system: $Ax=b$, where $A=I-\left|\lambda dt\right|W_{p}L$,~
$L$ is the Normalized TQLBO defined in the equation (\ref{eq:TQLBO-Normalized_Matrix}),
$x=V^{\prime}$ are the smoothing vertices, $b=V^{t}$ are the actual
vertices positions, $W_{p}$ is a diagonal matrix with weight vertex
group, and $\lambda dt$ is the enhancement factor that supports negative
and positive values: negative for enhancement and positive for smoothing.

The method was devised to use with weighted vertex groups, which specify
the final shape enhancement of the solution, meaning $0$ as no changes
and 1 when a maximal change is applied. The weights modify the influence
zones, where the Laplacian is applied, as shown in equation \ref{eq:Lineal_System_with_wp}.
Interestingly, the generated family of shapes may change substantially
with the weights of specific control points.

The curvature cannot be calculted at the boundary of the meshes that
are not closed, for that reason we use the scale-dependent operator
proposed by Desbrun et al. \cite{Desbrun1999}, the enhancement factor
for boundary is represented by $\lambda_{e}$.

@@

@@

\caption{\label{fig:Catmull_Clark}(a) Original Model, (b) Model with Catmull-Clark
Subdivision. Models with Laplacian smoothing: (c) and (d). Models
with a first Laplacian filtering $\lambda=60.0$, $\lambda_{e}=12.0$
and before applying shape enhancement: (e) and (f).}
\end{figure*}

A new sculpting brush is herein proposed and aims to inflate the shape,
magnifying the shape curvatures of a polygon mesh in real time. This
brush works properly with the stroke method \textsl{Drag Dot}, allowing
to pre-visualize the model changes before the mouse is released. Also,
it allows to move the mouse along the model to match the shape zone
which is supposed to be enhanced.

Brushes that perform a similar inflation can introduce mesh distortions
or produce mesh self-intersections, provided these brushes only move
the vertices along the normal without any global information. In contrast,
the present method searches for a proper inflation while preserving
the global curvature, retaining the original shape and main model
features. In addition, this method simplifies the work required for
the enhancement since it needs not different brushes for inflating,
softening or styling. The enhanced brush can make all these operation
in a single step. Real-time brushes require the Laplacian matrix is
constructed with the vertices that are within the sphere radius defined
by the user, reducing the matrix to be processed, the center of this
sphere depending on the place where the user clicks on the canvas
and the three-dimensional mesh placed where the click is projected.
Special handling is required for the boundary vertices with neighbors
that are not within the brush radius: these vertices are marked as
boundary and the curvature is not there calculated, but they must
be included in the matrix so that every vertex has their corresponding
neighbors within the selection. The sculpting Laplacian matrix reads
as.

@@

Catmull-Clark subdivision surface methods generate smooth and continuous
models from a coarse model and produce quick results because of the
simplicity of implementation. Nevertheless, changes to the global
curvature are hardly implantable. The Catmull-Clark subdivision surfaces
together with shape enhancement can easily generate families of shapes
by changing a single parameter, allowing to handle a model with very
few vertices. In practice, this would allow an artist to choose a
model from a similar set of options that would meet his/her needs
without having to change each of the control vertices. Likewise, the
presented method allows the use of vertex weight paint over the control
points. The weights can be applied to a coarse model, followed by
a Catmull-Clark subdivision where weights are interpolated, producing
weights with smooth changes in the influence zones, as shown in figure
\ref{fig:Subdivision-Cups}.c.

@@

The results of the shape enhancement method with the extension of
the Laplace Beltrami operator for hybrid quad/triangle meshes with
several example models (see figures \ref{fig:Spectrum}, \ref{fig:Subdivision-Cups},
\ref{fig:Catmull_Clark}, \ref{fig:TQLBO_test}, \ref{fig:camello_enhanced},
\ref{fig:Sculpt_Brush}, \ref{fig:Performance-sculpt}, \ref{fig:(a)Monkey},
\ref{fig:Animated_Camell}). The shape enhancement was assessed with
TQLBO method on a PC with AMD Quad-Core Processor @ 2.40 GHz and 8
GB RAM.

@@

Methods using the Catmull-Clark subdivision surface and the enhancement
allows to modify the curvature that is obtained with the process of
subdivision, as shown in figure \eqref{fig:Subdivision-Cups}. This
test used a coarse cup model, in which the subdivision was performed,
followed by a Laplacian smoothing and enhancement. In figure \eqref{fig:Subdivision-Cups}.c,
\eqref{fig:Subdivision-Cups}.d shows also the use of weight vertex
groups over coarse models, with subdivision surfaces that allowed
to generate the weights for the new interpolated vertices. These new
weights were used for the enhancement obtained on the 6 cups that
are at the right of the figure \eqref{fig:Subdivision-Cups}.d.

Laplacian smoothing applied with simple subdivision (see figure \ref{fig:Catmull_Clark}.b.)
may produce similar results to those obtained with Catmull-Clark (see
figure \ref{fig:Catmull_Clark}.c.), whose models are in average equal
triangles. The one obtained with the Laplacian smoothing is shown
in panel (c), (d) and those curvature modified versions are in (e)
and (f). As can be observed, different versions of the original sketch
can be obtained by parameterizing a single model value, a great advantage
of the presented method. Figure \ref{fig:camello_enhanced} shows
the generation of different versions of a camel according to the $\lambda$
parameter. In the top row, it is shown the shape enhancement results,
as $\lambda$ becomes larger and negative, the resultant shape is
observed as if the model would inflate the more convex parts, as shown
in figure \ref{fig:Spectrum}. The larger the $\lambda$ parameter
the larger the model feature enhancements. The bottom row of figure
\ref{fig:camello_enhanced} shows the use of weighted vertex groups,
specifying which areas will be enhanced. On the left, the enhancement
of the camel legs produces an organic aspect, notice that the border
is not distorted and smooth.

@@

\caption{\label{fig:camello_enhanced}Top row: Original camel model in left.
Shape enhancement with $\lambda=-30.0$, $\lambda=-100.0$, $\lambda=-400.0$.
Bottom row: Shape enhancement with weight vertex group, $\lambda=-50.0$
and 2 iterations for the legs, $\lambda=-200.0$ and 1 iteration for
the head and neck.}
\end{figure}

The enhancement of the silhouette features is predictable and invariant
under isometric transformations, as those classically used in some
animations (see Figure \ref{fig:Animated_Camell}). In this figure,
the animation shows some camel poses during a walk, the enhancement
is performed at the neck and legs, as shown in the bottom left camel
in figure \ref{fig:Animated_Camell}. Local modifications produced
by the pose interpolation or animation rigging practically do not
affect the result. In spite of at any pose of the camel legs there
is a clear difference, the enhancement method allows a flesh-like
shape in the original pattern produced by the artist. This is due
to the mesh restricted diffusion process so that small local changes
are treated without affecting the global solution. The method therefore
is rotation invariant since it depends exclusively on the normal mesh
field, which is rotation invariant.

Figure \ref{fig:Sculpt_Brush} shows the use of a shape enhancement
brush for sculpting in real time. One pass was used with the brush,
as shown in the figure, with the blue and red radius. In figure \ref{fig:Sculpt_Brush}.b
the camel foot shows the inflation intersection that looks like two
bubbles, a similar pattern to what is observed to the fingers on the
bottom of the same figure. The silhouette enhancement is observed
in figure \ref{fig:Sculpt_Brush}.c since the main shape is retained
together with its finger and foot details. Similar results can be
obtained by a user, however it would take several steps and require
the use of several brushes, while the shape enhancement took a single
step. Likewise, this new method can easily enhance organic features
like muscles during the sculpting process. In figure \ref{fig:Performance-sculpt}
the shape enhancement brush performance is illustrated, in this experiment
three models with 12K, 40K and 164K vertices, were used. These models
were sculpted with the shape enhance brush, at each step the brush
sphere containing a variable number of vertices for processing. The
processing time for 800 vertices in the camel paw (40k model) only
took 0.1 seconds, for 2600 vertices in the leg and neck (model 40k)
took 0.5 seconds, these times are suitable in real applications since
an artist sculpts a model for parts, and each part is represented
by an average of about 1800 vertices.

Tests with the Laplacian operator (equation \ref{eq:TQLBO_Simple_Matrix})
and its normalized version (equation \ref{eq:TQLBO-Normalized_Matrix}),
produce similar results if the triangles or quads that compose the
mesh are about the same size. The normalized version is more stable
and predictable because it is not divided by the area of the ring
which may be very small and causes numeric problems, as shown in figure
\ref{fig:(a)Monkey}.c bottom row. The shape enhancement of the model
with the normalized Laplacian operator results in a more regular pattern.
The model can be deformed with a TQLBO normalized version with large
$\lambda$ ($\lambda>400$) while intersecting itself with no peaks.
Figure \ref{fig:(a)Monkey}.c shows different results due to the quads
areas in the model. Quadss with larger area have smaller enhancement
(figure \ref{fig:(a)Monkey}.c skull), and smaller quads have larger
enhancements (figure \ref{fig:(a)Monkey}.c chin).

@@

\caption{\label{fig:Sculpt_Brush}Top row: (a) Leg Camel, (b) Inflate brush
for leg into blue circle, (c) Enhance shape brush for leg into red
circle. Bottom row: (a) Hand, (b) Inflate brush for fingers into blue
circle, (c) Shape enhancement brush for fingers in red circle.}
\end{figure}

@@

\caption{\label{fig:Performance-sculpt}Performance of our dynamic shape enhancement
brush in terms of the sculpted vertices per second. Three models with
12K, 40K, 164K vertices used for sculpting in real time.}
\end{figure}

@@

\caption{\label{fig:(a)Monkey}(a) Bottom row: Original Model. Top row: Original
model scaled by 4. (b) Top and bottom row: enhancing with Normalized-TQLBO
$\lambda=-50$ (c) Top and bottom row: enhancing with TQLBO $\lambda=-50$.}
\end{figure}

@@

\caption{\label{fig:Animated_Camell}The method is pose insensitive. The enhancement
for the different poses are similar in terms of shape. Top row: Original
walk cycle camel model. Bottom row: Shape enhancement with weight
vertex group, $\lambda=-400$ and $2$ iterations. }
\end{figure*}

>>>>

%------------------------------------------------------------------------- 
% change the % on next lines to produce the final camera-ready version 
\newif\iffinal
\finalfalse
%\finaltrue
\newcommand{\jemsid}{99999}
%-------------------------------------------------------------------------

@@

Interest in meshes composed of triangles and quads has lately increased
because of the flexibility of modeling tools such as Blender 3D \cite{blender}.
Nowadays, many artists use a manual connection of a couple of vertices
to perform animation processes and interpolation \cite{Mullen2007}.
It is then of paramount importance to develop operators that easily
interact with such meshes, eliminating the need of preprocessing the
mesh to convert it to triangles. The shape inflation and shape exaggeration
can thus be used as such brush in the sculpting process, when inflating
a shape since current brushes end up by losing detail when moving
vertices \cite{Stanculescu2011}. In contrast, the presented method
inflates a mesh by moving the vertices towards the reverse curvature
direction, conserving the shape and sharp features of the model.

%------------------------------------------------------------------------- 
\paragraph*{Contributions}
%
This work presents an extension of the Laplace
Beltrami operator for hybrid quad/triangle meshes, representing a
larger mesh spectrum from what has been presented so far. The method
eliminates the need of preprocessing and allows preservation of the
original topology. Likewise, along with this operator, it is proposed
a method to generate a family of parameterized shapes, in a robust
and predictable way. This method enables customization of the smoothness
and curvature, obtained during the subdivision surfaces process. Finally,
it is proposed a new brush for inflating the silhouette mesh features
in modeling and sculpting.

This work is organized as follows: Section \ref{sub:1.1-Related-work}
presents works related to the Laplacian mesh processing, digital sculpting,
and offsetting methods for polygonal meshes; In section \ref{sec:Laplacian-Smooth}
, it is described the theoretical framework of the Laplacian operator
for polygon meshes; In section \ref{sec:Proposed-Method}, it is presented
the method for shape inflation and applications of subdivision of
surfaces and sculpting; finally some Laplacian operator results, to
hybrid quad/triangle meshes are graphically shown as well as results
of the shape inflation applications in sculpting, subdivision and
modeling.

@@

Offset methods for polygon meshing, based on the curvature defined
by the Laplace Beltrami operator, have been developed. These methods
adjust the shape offset by a constant distance, with enough precision. Nevertheless, these methods fail
to conserve sufficient detail because of the smoothing, a crucial
issue which depends on the offset size \cite{Zhuo2012}. In volumetric
approaches, in case of point-based representations, the offset boundary
computation is based on the distance field and therefore when calculating
such offset, the topology of the model may be different to the original
\cite{Chen2011}.

\cite{Gal2009} propose automatic feature detection and shape edition
with feature inter-relationship preservation. They define salient
surface features like ridges and valleys, characerized by their first
and second order curvature derivatives, see \cite{Ohtake2004}, and angle-based
threshold. Likewise, curves have been also classified as planar or
non-planar, approximated by lines, circles, ellipses and other complex
shapes. In such case, the user defines an initial change over several
features which is propagated towards other features, based on the
classified shapes and the inter-relationships between them. This method
works well with objects that have sharp edges, composed of basic geometric
shapes such as lines, circles or ellipses. However, the method is
very limited when models are smooth since it cannot find the proper
features to edit.

@@

The \textit{Laplace Beltrami operator} LBO noted as $\triangle$
is used for measuring the mean curvature normal to the Surface $S$
\cite{Pinkall1993}.

\begin{equation}
%\triangle_{g}S=2\kappa\mathbf{n}\label{eq:def_LBO}
\triangle S=2\kappa\mathbf{n}\label{eq:def_LBO}
\end{equation}

The LBO has desirable properties: the LBO points out to the direction
of the minimal surface area.

@@

\begin{equation}
\triangle_{S}\left(v_{i}\right)=2\kappa\mathbf{n}=\frac{\nabla A}{A}=\underset{v_{j}\in N_{1}\left(v_{i}\right)}{\frac{1}{2A}\sum}w_{ij}\left(v_{j}-v_{i}\right)
\end{equation}

@@

\subsection{The Shape Inflation\label{sub:Curvature-Enhancing}}

@@

\caption{\label{fig:Subdivision-Cups} Family of cups generated with our method,
from a coarse model (a), (c): the shape, obtained from the Catmull-Clark
Subdivision (b), (d), is inflated. Soft constraints, over the coarse
model, is drawn in red and blue (c).}

@@

The shape is inflated by using the reverse direction of the curvature
flow, moving the vertices towards those mesh portions with larger
curvature. A standard diffusion process is applied:

@@

The vertices $V^{t+1}$ are inflated, along their reverse curvature
direction, by solving the linear system: $Ax=b$, where $A=I-\left|\lambda dt\right|W_{p}L$,~
$L$ is the Normalized TQLBO defined in the equation (\ref{eq:TQLBO-Normalized_Matrix}),
$x=V^{\prime}$ are the smoothing vertices, $b=V^{t}$ are the actual
vertices positions, $W_{p}$ is a diagonal matrix with vertex weights,
 and $\lambda dt$ is the inflate factor that supports negative
and positive values: negative for inflation and positive for smoothing.

The method was devised to use with weighted vertex groups, which specify
the final shape inflation of the solution, meaning $0$ as no changes
and 1 when a maximal change is applied. The weights modify the influence
zones, where the Laplacian is applied, as shown in equation \ref{eq:Lineal_System_with_wp}.
Interestingly, the generated family of shapes may change substantially
with the weights of specific control points.

The curvature cannot be calculted at the boundary of the meshes that
are not closed, for that reason we use the scale-dependent operator
proposed by Desbrun et al. \cite{Desbrun1999}, the inflation factor
for boundary is represented by $\lambda_{e}$.

@@

The shape inflation use a negative curvature flow that is an unstable process 
when performing many iterations, however, our method uses less than 3 
iterations to get good results, and with 3 iterations or less the method behaves stable.

@@

\caption{\label{fig:Catmull_Clark}(a) Original Model, (b) Model with Catmull-Clark
Subdivision. Models with Laplacian smoothing: (c) and (d). Models
with a first Laplacian filtering $\lambda=60.0$, $\lambda_{e}=12.0$
and before applying shape inflation: (e) and (f).}
\end{figure*}

A new sculpting brush is herein proposed and aims to inflate the shape,
magnifying the shape curvatures of a polygon mesh in real time. This
brush works properly with the stroke method \textsl{Drag Dot}, allowing
to pre-visualize the model changes before the mouse is released. Also,
it allows to move the mouse along the model to match the shape zone
which is supposed to be inflated.

Brushes that perform a similar inflation can introduce mesh distortions
or produce mesh self-intersections, provided these brushes only move
the vertices along the normal without any global information. In contrast,
the present method searches for a proper inflation while preserving
the global curvature, retaining the original shape and main model
features. In addition, this method simplifies the work required for
the inflation since it needs not different brushes for inflating,
softening or styling. The inflated brush can make all these operation
in a single step. Real-time brushes require the Laplacian matrix is
constructed with the vertices that are within the sphere radius defined
by the user, reducing the matrix to be processed, the center of this
sphere depending on the place where the user clicks on the canvas
and the three-dimensional mesh placed where the click is projected.
Special handling is required for the boundary vertices with neighbors
that are not within the brush radius: these vertices are marked as
boundary and the curvature is not there calculated, but they must
be included in the matrix so that every vertex has their corresponding
neighbors within the selection. The sculpting Laplacian matrix reads
as.

@@

Catmull-Clark subdivision surface methods generate smooth and continuous
models from a coarse model and produce quick results because of the
simplicity of implementation. Nevertheless, changes to the global
curvature are hardly implantable. The Catmull-Clark subdivision surfaces
together with shape inflation can easily generate families of shapes
by changing a single parameter, allowing to handle a model with very
few vertices. In practice, this would allow an artist to choose a
model from a similar set of options that would meet his/her needs
without having to change each of the control vertices. Likewise, the
presented method allows the use of vertex weight paint over the control
points. The weights can be applied to a coarse model, followed by
a Catmull-Clark subdivision where weights are interpolated, producing
weights with smooth changes in the influence zones, as shown in figure
\ref{fig:Subdivision-Cups}.c.

@@

The results of the shape inflation method with the extension of
the Laplace Beltrami operator for hybrid quad/triangle meshes with
several example models (see figures \ref{fig:Spectrum}, \ref{fig:Subdivision-Cups},
\ref{fig:Catmull_Clark}, \ref{fig:TQLBO_test}, \ref{fig:camello_enhanced},
\ref{fig:Sculpt_Brush}, \ref{fig:Performance-sculpt}, \ref{fig:(a)Monkey},
\ref{fig:Animated_Camell}). The shape inflation was assessed with
TQLBO method on a PC with AMD Quad-Core Processor @ 2.40 GHz and 8
GB RAM.

@@

Methods using the Catmull-Clark subdivision surface and the inflation
allows to modify the curvature that is obtained with the process of
subdivision, as shown in figure \eqref{fig:Subdivision-Cups}. This
test used a coarse cup model, in which the subdivision was performed,
followed by a Laplacian smoothing and inflation. In figure \eqref{fig:Subdivision-Cups}.c,
\eqref{fig:Subdivision-Cups}.d shows also the use of weight vertex
groups over coarse models, with subdivision surfaces that allowed
to generate the weights for the new interpolated vertices. These new
weights were used for the inflation obtained on the 6 cups that
are at the right of the figure \eqref{fig:Subdivision-Cups}.d.

Laplacian smoothing applied with simple subdivision (see figure \ref{fig:Catmull_Clark}.b.)
may produce similar results to those obtained with Catmull-Clark (see
figure \ref{fig:Catmull_Clark}.c.), whose models are in average equal
triangles. The one obtained with the Laplacian smoothing is shown
in panel (c), (d) and those curvature modified versions are in (e)
and (f). As can be observed, different versions of the original sketch
can be obtained by parameterizing a single model value, a great advantage
of the presented method. Figure \ref{fig:camello_enhanced} shows
the generation of different versions of a camel according to the $\lambda$
parameter. In the top row, it is shown the shape inflation results,
as $\lambda$ becomes larger and negative, the resultant shape is
observed as if the model would inflate the more convex parts, as shown
in figure \ref{fig:Spectrum}. The larger the $\lambda$ parameter
the larger the model feature inflations. The bottom row of figure
\ref{fig:camello_enhanced} shows the use of weighted vertex groups,
specifying which areas will be inflated. On the left, the inflation
of the camel legs produces an organic aspect, notice that the border
is not distorted and smooth.

@@

\caption{\label{fig:camello_enhanced}Top row: Original camel model in left.
Shape inflation with $\lambda=-30.0$, $\lambda=-100.0$, $\lambda=-400.0$.
Bottom row: Shape inflation with weight vertex group, $\lambda=-50.0$
and 2 iterations for the legs, $\lambda=-200.0$ and 1 iteration for
the head and neck.}
\end{figure}

The inflation of the silhouette features is predictable and invariant
under isometric transformations, as those classically used in some
animations (see Figure \ref{fig:Animated_Camell}). In this figure,
the animation shows some camel poses during a walk, the inflation
is performed at the neck and legs, as shown in the bottom left camel
in figure \ref{fig:Animated_Camell}. Local modifications produced
by the pose interpolation or animation rigging practically do not
affect the result. In spite of at any pose of the camel legs there
is a clear difference, the inflation method allows a flesh-like
shape in the original pattern produced by the artist. This is due
to the mesh restricted diffusion process so that small local changes
are treated without affecting the global solution. The method therefore
is rotation invariant since it depends exclusively on the normal mesh
field, which is rotation invariant.

Figure \ref{fig:Sculpt_Brush} shows the use of a shape inflation
brush for sculpting in real time. One pass was used with the brush,
as shown in the figure, with the blue and red radius. In figure \ref{fig:Sculpt_Brush}.b
the camel foot shows the inflation intersection that looks like two
bubbles, a similar pattern to what is observed to the fingers on the
bottom of the same figure. The silhouette inflation is observed
in figure \ref{fig:Sculpt_Brush}.c since the main shape is retained
together with its finger and foot details. Similar results can be
obtained by a user, however it would take several steps and require
the use of several brushes, while the shape inflation took a single
step. Likewise, this new method can easily inflate organic features
like muscles during the sculpting process. In figure \ref{fig:Performance-sculpt}
the shape inflation brush performance is illustrated, in this experiment
three models with 12K, 40K and 164K vertices, were used. These models
were sculpted with the shape inflate brush, at each step the brush
sphere containing a variable number of vertices for processing. The
processing time for 800 vertices in the camel paw (40k model) only
took 0.1 seconds, for 2600 vertices in the leg and neck (model 40k)
took 0.5 seconds, these times are suitable in real applications since
an artist sculpts a model for parts.
%, and each part is represented by an average of about 1800 vertices.

Tests with the Laplacian operator (equation \ref{eq:TQLBO_Simple_Matrix})
and its normalized version (equation \ref{eq:TQLBO-Normalized_Matrix}),
produce similar results if the triangles or quads that compose the
mesh are about the same size. The normalized version is more stable
and predictable because it is not divided by the area of the ring
which may be very small and causes numeric problems, as shown in figure
\ref{fig:(a)Monkey}.c bottom row. The shape inflation of the model
with the normalized Laplacian operator results in a more regular pattern.
The model can be deformed with a TQLBO normalized version with large
$\lambda$ ($\lambda>400$) while intersecting itself with no peaks.
Figure \ref{fig:(a)Monkey}.c shows different results due to the quads
areas in the model. Quadss with larger area have smaller inflation
(figure \ref{fig:(a)Monkey}.c skull), and smaller quads have larger
inflations (figure \ref{fig:(a)Monkey}.c chin).

@@

\caption{\label{fig:Sculpt_Brush}Top row: (a) Leg Camel, (b) Inflate brush
for leg into blue circle, (c) Inflate shape brush for leg into red
circle. Bottom row: (a) Hand, (b) Inflate brush for fingers into blue
circle, (c) Shape inflation brush for fingers in red circle.}
\end{figure}

@@

\caption{\label{fig:Performance-sculpt}Performance of our dynamic shape inflation
brush in terms of the sculpted vertices per second. Three models with
12K, 40K, 164K vertices used for sculpting in real time.}
\end{figure}

@@

\caption{\label{fig:(a)Monkey}(a) Bottom row: Original Model. Top row: Original
model scaled by 4. (b) Top and bottom row: inflating with Normalized-TQLBO
$\lambda=-50$ (c) Top and bottom row: inflating with TQLBO $\lambda=-50$.}
\end{figure}

@@

\caption{\label{fig:Animated_Camell}The method is pose insensitive. The inflation
for the different poses are similar in terms of shape. Top row: Original
walk cycle camel model. Bottom row: Shape inflation with weight
vertex group, $\lambda=-400$ and $2$ iterations. }
\end{figure*}
